This is the Title

### 2017-03-15 trunk/abc/paper/paper.tex
Implement sizeof; more paper writing
Thread context through tocil routines. Elaborate struct types, but not actually supporting them yet. Remove 'width' parameter from translvalue continuation, since it is redundant. Some paper hacking. Extremely simple structs test.

Truly self-documenting
Giving new meaning to "program committee" "evaluating" my paper
For good reasons that I will explain later...

@@

missing condition; ``left-facing''

@@

@@

>>>>

Truly self-documenting
For good reasons that I will explain later...

@@

@@

songs to do: https://www.youtube.com/watch?v=EJkJbUbvYJA

In video: show error in intel manual http:\\www.intel.com

@@

XXX: Should really write about PSP.
could write about optimizing the value table

Ideas for improvement before paper's submitted:
 - Implement 'void' return type
 - Make int literals actually 16 bit for now?
 - Implement multiplication and division
 - Implement switch
 - in paper.c, support multichannel sound.
 - implement sbrk primitive (just returns 0x8000?)
